\documentclass{article}

\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{braket}

\title{Squeezed states on a molecule chip}

\author{Cameron McGarry}

\begin{document}

\maketitle

We aim to create squeezed spin states on a molecule chip. I think this is
possible by employing a quantum non-demolition (QND) measurement on a two-level
system in the magnetic trap. In this white paper I will explain in general how
a QND measurement can be performed by coupling a spin-two system to a cavity,
and how squeezed spin states can be created in such a system. I will then
describe how this could be implemented on a chip trap with calcium monofluoride
(CaF) molecules. Set $\hbar=1$ because this is theory and I am a very serious
physicist.

\section{System of many spins}

% Need to explicitly say that |g> and |e> are eigenstates of sigma_z and s^2?
In general we consider a two level system with ground and excited staes $\ket{g}$
and $\ket{e}$ respectively, with a transition frequency $\omega_0$. For a
system of $N$ such spins, the $i^\text{th}$ spin has a spin operator

\begin{math}
\mathbf{s}_i = \frac{1}{2}\begin{bmatrix} \sigma^i_x \\ \sigma^i_y \\sigma^i_z
\end{bmatrix}
\end{math}

where $\sigma^i_j$ represents a Pauli matrix. The collective spin operator is
then

\begin{math}
\mathbf{S} = \sum_{i=1}^N \mathbf{s}_i
\end{math}

having individual components

\begin{math}
S_j = \sum_{i=1}^N \frac{1}{2} \sigma_j^i.
\end{math}

In free space, the system of spins evolves according to the Hamiltonian

\begin{math}
H_0 = \frac{1}{2}\omega_0 S_z.
\end{math}

For our QND measurement we will couple the spins to a cavity, it will be
instructive to explore the dynamics in the cavity in a general way. The
resulting Hamiltonian is $H = H_0 + H_\text{cav} + H_\text{int}$ where

\begin{math}
H_\text{cav} = \omega a^\dagger a
\end{math}

describes the cavity photons, with frequency $\omega$ and annihilation
operator $a$, and

\begin{math}
H_\text{int} = \Omega c^\dagger c S_z
\end{math}

% TODO Proper Ref. cite command here
describes the interaction of the spins with the light. This interaction term is
only valid for low photon number in the cavity, that is $\expectation{c^\dagger
c} \lleq \(\Delta/g)^2$ as explained in reference~\cite{SchleierSmith2011}.

In the case
of a single spin, the coupling would be the vacuum Rabi frequency

\begin{math}
\Omega_i = 2g_i = \mathbf{d}. \mathbf{\mathcal{E}}
\sqrt{\frac{\omega}{2\epsilon_0 V}}
\end{math}

where $\mathbf{d}$ is the dipole moment of the system, $\mathbf{\mathcal{E}}$
is the electric field vector at the spin, $V$ is the cavity mode volume and
$\epsilon_0$ is the permittivity of free space. For our collection of spins

\section{Performing quantum non-demolition measurements}

The idea of a QND measurement is, as the name suggests, to gain some knowledge
of the state of the system without collapsing the superposition.

\section{Squeezing with quantum non-demolition measurement}


\section{Implementation on CaF chip}

For our two-level
system in CaF choose the states $\ket{g} = \ket{N=0, F=1, m_F=1}$ and $\ket{e}
= \ket{1, 2, 2}$ for their long lifetime in a magnetic trap. The transition has
frequency $\omega_0/2\pi = \SI{20.5}{\giga\hertz}$ \cite{Williams2018}.

\section{Further thoughts: collective cavity cooling}

% I don't think that it's sufficient to just have the sideband cooling scheme
% described in the Andr\'e paper. We need to consider the effect of having a
% collective of spins, as is described for atoms in chapter 8 of reference
% \cite{SchleierSmith2011}

\section{Further thoughts: collision squeezing}

In addition to squeezing by QND measurement, atomic spin squeeze states have
been generated due to inter-atomic collisions \cite{}. These collisions
introduce a non-linear Hamiltonian term $H=\chi S_z^2$, which leads to a
shearing of the coherent state around the Bloch sphere around the $S_z$ state
\cite{}.

With our knowledge of collisions between atoms and molecules (or molecules and
molecules) might it be possible to generate squeezed states in atom-molecule
clouds, or very dense clouds of molecules? The latter could perhaps be explored
on the new CaF Bose-Einstein condensate apparatus.

\end{document}
