Cold atoms and molecules are a promising architecture for the implementation of
new quantum technologies. They have been used for devices in fields of
measurement~\cite{Campbell90}, simulation~\cite{Gross995} and testing of
fundamental physics~\cite{DeMille990}. However, one of the
main disadcantages when compared to, for example,
superconductor~\cite{Wallraff2004} or
optical~\cite{https://arxiv.org/abs/1707.02925} systems is the lack of
scalaibility and miniaturization.~\cite{nielsenandchuang}

In 1995, Weinstein and Libbrecht proposed an experiment for
studying cold atoms in environments with extremely high magnetic
gradients.~\cite{PhysRevA.52.4004} These gradients can be obtained by using
microfabricated wires in combination with a biasing field to form a trap above
a surface. Not only does this lead to an interesting environment for studying
new physics, but it introduces miniaturization into the cold-atom
toolkit.~\cite{2011Ac} There is also potential for integration of atomic or
molecular systems on a chip with other chip-based quantum
systems.~\cite{2011Ac, Kubo2011}

The first atomic chip trap was demonstrated four years later by Reichel et
al.~\cite{Reichel1999}. Their chip trap was shown to be a robust environment for
atomic experiments. The field of atom chips has since expanded~\cite{2011Ac},
with use as an architecture for creation of Bose-Einstein condensates being of
particular interest to many physicists.~\cite{Ott2001}

Although laser cooling of atoms has been commonplace since the late
20\textsuperscript{th} century, cooling of molecules has taken longer to develop
due to their more complex internal energy structure. However, this same rich
energy structure and other features of the molecules could be exploited to
produce new interesting technologies.~\cite{Tarbutt2018} We are now able to
produce \CaF molecules cooled below the Doppler limit~\cite{Truppe2017},
coherently control the states of such molecules~\cite{PhysRevLett.120.163201}
and load molecules into a tweezer array.~\cite{Anderegg2019} These developments
open the door to the realization of a molecule chip.

A proposal by Andr\'e et al. in 2006~\cite{Andre2006} suggested that integrating
an electrostatic trap with a micorwave field, both integrated on a chip would be
a powerful architecture, owing to the high coupling between rotational states of
the molecule and the microwave field (orders of magnitude greater than coupling
between microwaves and the hyperfine structure of an atom). This was years before
the first molecular MOT was created~\cite{Barry2014}. and recent developments
suggest that an electrostatic trap is not necessary. There are magnetically
insesitive rotational transitions in \CaF that are prime candidates for a qubit
transition on a chip.~\cite{} \cm{Need 20GHz and 40GHz citations}

In the following subsections I will discuss further the field of ultra-cooling
of atoms molecules, and the need for a molecule chip. The rest of the report
will focus on chip trapping, the design of our molecule chip for \CaF and the
outlook for the remainder of the project.

\subsection{Laser cooling of atoms and molecules}
\label{intro:lasercool}

A brief discussion of laser cooling is presented here. More detailed discussion
can be found in references~\cite{Metcalf1999,RevModPhys.70.721,McCarron_2018}.

The basic principle of laser cooling of atoms is to deflect atoms from their
trajectory by transfer of momentum from the laser light (radiation
pressure).~\cite{RevModPhys.70.721} Consider a moving atom with a
pre-chosen cooling transition between two internal states.  When such an atom
encounters a counter-propogating resonant photon absorption can take place,
reducing the atom's momentum. The atom can re-emit the photon in any direction,
but on average the resulting atom will be slower than before the encounter.
This process is known as Doppler cooling, as the light must be detuned from
resonance to account for Doppler shift experienced by the moving
molecule.~\cite{Metcalf1999}

Of course, the assumption of a two-level system is a vast simplification.  A key
example is sodium, where the hyperfine transition $3S_{1/2}\, (F=2) \rightarrow
3P_{3/2}\, (F'=3)$ transition was used to demonstrate this technique. However,
since the excited states of sodium have decay channels into $F=1$, it is
possible for atoms to fall into this state and out of resonance with the
cooling transition.  This can be overcome by introducing repumping light to
transfer atoms in dark states back into light states.~\cite{RevModPhys.70.721}

Most atom sources produce a beam, with typical velocities of a few
\SI{100}{\metre\per\second}.~\cite{Metcalf1999,}  As the atoms are slowed, the
Doppler shift they experience will change, and hence they will move out of
resonance with the transition.~\cite{RevModPhys.70.721} This can be overcome by
introducing chriped light~\cite{Prodan1984} or varying the transition frequency
by control of an external splitting field~\cite{PhysRevLett.48.596}.

An optical molasses can be formed from a pair of counter-propogating laser
beams, both red-detuned from the cooling transition. If the atom moves towards
either beam it will move into resonace and experience a pressure back towards
the trap centre. A set of three perpendicular optical molasses can cool an atom
in each direction, reducing the temperature but not providing any trapping
force~\cite{Metcalf1999} . Further cooling can be achieved in an optical
molasses by choosing the polarization of the light such that there is a
polarization gradient. This sub-Doppler cooling allows atoms to be cooled to the
lowest limit, the recoil temperature of the atoms (typically a few
\cm{\si{\micro\kelvin}}).~\cite{Dalibard:89}

Trapping can be achieved (for example) by optically pumping the atoms into a
weak-field seeking state and aplying a magnetic field to form either a
quadrupole~\cite{PhysRevLett.54.2596} or
Ioffe-Pritchard~\cite{PhysRevLett.51.1336} trap. Magnetically trapped atoms can
be further cooled by evaporation, which can ultimately be used to form a
Bose-Einstein condensate.~\cite{Anderson198} A quadrupole trap combined with an
optical molasses forms a magneto-optical trap (MOT) in which atoms are
simultaneously trapped by the magnetic field and cooled by the
lasers.~\cite{PhysRevLett.59.2631}

The MOT has become a fundamental component of many cold atom experiments, a vast
field which we cannot explore in any level of detail here. Of particular note to
us are experiments involving dipole trapping~\cite{PhysRevA.47.R4567}, such as
those in an optical lattice~\cite{Bakr2009} or tweezer~\cite{Ashkin:86}. Control
of the atomic states in a lattice has been used to perform quantum
simulation~\cite{Gross995} and to precisely measure the
second~\cite{Campbell90}.

The rich energy structure of molecules, having rotational and vibrational
degrees of freedom, makes cooling procedures more involved~\cite{Tarbutt2018},
but there are numerous properties of molecules that could be expolited in a
range of applications. The large electric dipole moment of some diatomic
molecules means that they interact more strongly with electric fields than
atoms, making an optical lattice of molecules, or a molecule on a chip, a good
candidate for scalable quantum simulation or computing~\cite{Micheli2006,
Andre2006}. Collisions between cold molecules could allow investigation of the
nature of quantum chemistry~\cite{Krems2008}, and cooled \cm{YbF} is being
developed to precisely measure the electron electric dipole moment as a means of
testing fundamental theories of physics~\cite{Lim2018}.

The tools developed for creation of cold atoms can be
directly applied to producing cold molecules. A MOT of \cm{$Rb85?$} and
\cm{$Cs133?$} can be used to form \cm{$RbCs$} via an interspecies Feshbach
resonance~\cite{PhysRevA.85.032506, PhysRevA.89.033604} and then transfered into
the ro-vibrational ground state by stimulated Raman adiabatic passage
(STIRAP).~\cite{PhysRevLett.113.255301, RevModPhys.70.1003}.

Alternatively, direct cooling of molecules can be performed, with notable
achivements for diatomic molecules.~\cite{Shuman2010} Beams of \cm{SrF} and
\cm{CaF} have been slowed with chirped light~\cite{PhysRevLett.108.103002,
Truppe2017a} and held in a MOT~\cite{Barry2014, Williams2017}. Sub-Doppler
cooling~\cite{Truppe2017} and coherent control of the rotational
state~\cite{PhysRevLett.120.163201,Blackmore_2018} have been demonstrated for
\cm{CaF}. Early experiments with optical tweezers have also been
performed~\cite{Anderegg2019}.

\cm{Should also mention Stark decelerators to prep for molecule chips.
Mentioning Zeeman decelerators would also be nice for completeness.}

\cm{
Ongoing experiments with CaF will investigate the potential for sympathetic
cooling with Rb atoms, and further explore the fidelity of qubits based on
microwave transitions in the molecule. These experiments will pave the way for a
chip, by providing the phase space density for efficient loading and
computational basis for an on-chip qubit respectively.~\cm{How to cite this
incomplete work? QSUM?}
%
%
In this report, we will discuss the 
}

\subsection{Structure of this report}

In this document, I will outline the ongoing progress in the design and
implementation of a molecular chip trap. In section \ref{litrev} I will present
the existing research that has been undertaken in the fields of atomic and
molecular chip traps. Next, section \ref{experiment} will discuss the design
process for our experiment, and the various engineering challenges that we have
had to overcome. Finally I will present the outlook for the remainder of the
project, including some \cm{stretch goals??}
