At the time of the original molecule chip proposal~\cite{Andre2006}, to see atom
chips had been loaded using a magneto-optical trap (MOT) as a
source~\cite{Reichel1999, Ott2001}, however a molecule MOT had not yet been
built, and there was no credible source of loading a chip of this
type.\footnote{\cm{Flyover chips had been created, maybe something about PSD
meant a beam wouldn't work? expand in body}}
%
Today we have access to molecules cooled below the Doppler
temperature~\cite{Truppe2017}, with potential for further sympathetic cooling
with rubidium~\cm{how to cite this?}. Further technologies for loading a
molecule chip, such a optical tweezers~\cite{Liueaar7797} have also been
demonstrated.

These developments have made the implementation of a molecule chip feasible. In
this section, we will review the state of the field, including work on atom
chips and these supporting technologies.

\subsection{Atom chips}

% Take-away points:
%   Magnetic trap
%   How to get CPW on (Bohi)
%   MTT + big U to load is viable
%   Required PSD???

In developing the molecule chip, we have been able to draw upon the
well-developed field of atom chips to inform our design choices. Let us consider
three different aspects of chip design: trapping on the chip, loading into this
trap, manipulation of trapped atoms or molecules.

\subsubsection{Chip traps}

The Andr\'e proposal~\cite{Andre2006} suggests the use of an electrostatic trap
to contain the molecules, however this is not the only option available. In
fact, magnetic trapping of atoms is much more widely explored.~\cite{2011Ac}.
\cm{more cites here!} In addition, we will see in section~\cm{reference CPW
discussion}% TODO
that the electrostatic trap is not achievable in our intended design. As such we
will focus in this section on magnetostatic trapping of atoms above a chip.

% TODO Continue this

\subsubsection{Loading}

Folman et al.~\cite{Folman2000} were one of the first to demonstrate mirror-MOT
loading, where the surface of the chip is used as the mirror to from a MOT close
to the surface. The mirror-MOT held $10^8$ \cm{7\^Li} atoms, and was formed of
four laser beams, with two reflected off the chip, making the six beams in total
that are required for trapping. The magnetic field is generated by coils in
anti-Helmholtz configuration, which are switched off in favour of a large
U-shaped wire, which provides a quadrupole field whose zero is aligned with the
chip. This is a very common scheme to bring atoms close to the chip
surface~\cite{Reichel1999, PhysRevLett.97.200405, 2011Ac, Boehi2009}, however it
has also been shown~\cite{0256-307X-25-9-034} that it is possible to forego the
coil MOT and load atoms directly from a MOT formed by a U-wire.

After establishing a mirror-MOT, Folman et al. changed the bias field in order
to bring the cloud closer to the surface. They then turn off the lasers so that
the trapping is purely magnetic, and transfer to the trapping
wires on the chip. An adiabatic change of the bias fields can then be used to
draw the atoms closer to the surface~\cite{Reichel1999}. In the case of a
straight wire trap and hence \myeqref{TODO}, to increase the bias field will
also decrease the trapping height.

This principle can be extended to more complex trap types and varying the
currents through the trapping wires trapping.~\cite{Folman2000} It is also
possible to construct a series of wire traps in close proximity, whose currents
can then be independently controlled such that the trap centre is moved between
them. This allows the use of higher currents through wide wires when the cloud
is far from the surface, but a smaller wire must be used when the atoms are
close to it, so that the approximation of an infinitesimally small wire remains
accurate.

This adiabatic change of currents (through various wires) and bias fields is
another common step in the loading procedure~\cite{Folman2000,2011Ac,
RevModPhys.79.235} and can also be used to transport atoms above the
surface~\cite{Reichel1999, Schwindt2005}. Bringing the trap centre close to the
surface also compresses the atom cloud, and since the compressing force is
conservative~\cm{TODO: cite}, this leads to adiabatic heating of the cloud.
Conservation of phase space density suggests that the final temperature will be
given by~\cite{Metcalf1999}
\cm{TODO: check this cite is legit}
%
\begin{equation}
   T_1 = T_0\left(\frac{V_0}{V_1}\right)^\frac{2}{3}.
\end{equation}

After compression, the likelihood of collisions between the atoms is increased,
which results in the loss of large numbers of atoms due to inelastic collisions.
The solution to this, as presented by B\"ohi et al.~\cite{Boehi2009} is to
evaporatively cool atoms in the larger traps, before transferring them into the
smaller traps. The magnetic traps are compressed to increase the collision
rates and then a radio frequency (RF) ramp is applied to remove the hottest
atoms from the trap, thus reducing the total energy and increasing the number of
atoms that will be accepted into the next (smaller) trap.~\cite{Foot2005,
Metcalf1999}

Also of note is the possibility of forming a MOT from a single laser beam using
a patterned wafer~\cite{Nshii2013}. This eliminates the need for multiple beams
to create a mirror-MOT. This has the benefit of offering a stable and highly
reproducible MOT for loading.

Direct loading of a chip with an optical tweezer is also a possibility for
transferring molecules directly onto a chip~\cite{Liueaar7797}, with Bernon et
al.~\cite{Bernon2013} having demonstrated the technique with atoms. In this
experiment, an optical tweezer transport a cloud of $5\times10^6$ \cm{87\^Rb}
atoms from a MOT onto a chip trap \SI{40}{\milli\metre} away. This has the
benefit of insignificant losses and heating. This is a very attractive option
for loading, but molecular optical tweezers are still in their
infancy~\cite{Anderegg2019}, so this is left as a possibility for future
research.

\subsubsection{Manipulation in the trap}


\subsection{Cold molecule sources}

Note that every one \cm{check this is the case} of the above loading methods for
chips begins with an atomic MOT. Whilst there do exist atom~\cite{Dekker2000},
and even molecule chips~\cite{Bethlem2000. Meek2008} that don't rely on a MOT,
it seems that having a molecular MOT will vastly increase the loading schemes
available to use. At the time of Andr\'e's proposal~\cite{Andre2006}, this had
not been achieved, but today molecular MOTs, and even sub-Doppler cooling of
molecules has been achieved, as we will discuss below.

\subsection{Molecule chips}

\subsection{Fabrication methods}

% Photolith
% Electroplating
% Multilayers
