%\thispagestyle{empty}
\begin{singlespace}
Of course I must thank my supervisors. Both of you have displayed limitless
patience with me. Ben, you are a font of infinite wisdom in the lab, and have
tolerated my bush-league attempts at lab work, and your help in navigating the
realities of academic life is hugely appreciated. Mike, you are an incredibly
commited individual, and the fact that you constantly made time for me despite
your immensely busy schedule has not gone amiss. Thank you in particular for
reading and re-reading this thesis.
%
To both of you, I echo the various leaving speeches that I have heard through
my time here: your greatest accomplishment is maintaing a research group that
is committed, hard-working and most importantly, a welcoming place to work.
I am enormously grateful to both of you for everything you have taught me.

To the other members of the Centre for Cold Matter, I also thank you for making
my time as a PhD student educational and enjoyable. Without you it would not
have been possible. In particular those of you working on the \CaF{}
experiment, who have also exercised great patience with me, and given me
the time and space that I needed to attempt my final measurements. I wish you
all the best as you continue developing the experiment. Thanks go in particular
to those of you who worked on the chip experiment with me:
Bharath Srivathsan, who has helped in the design process, and worked
with me on the fabrication process and  Kyle Jarvis, who designed the holding-chip,
undertook many COMSOL simulations of CPWs. 
% TODO Gautam for help with RROC?
%
I must also mention Sanja Maricic
and Miranda Toora, who have been \cm{incredibly patient} with my various inane
requests.

This project has been aided by a number of external collaborators. Mainly the
staff at the London Centre for Nanotechnology, who have been enormously helpful
regarding microfabrication, especially Steve Etienne and Vj Krishnan. Towards
the end of my studies we received beautiful chips microfabricated by Amado
\cm{Bautista} and his colleagues at \cm{the university of Hannover}. I hope
that someone is able to pick up my torch and use these to develop a fantastic
\CaF{} chip experiment.

I am grateful to have a wide circle of people to complain to when things have
gone wrong.  First, the bored gamers: Aniq, Cathy, Jason, Jay and Yuki, whose
incessant banter kept me sane when locked indoors for weeks at a time. When we
were allowed to be together I enjoyed many an evening in the pub with my fellow
members of the Controlled Quantum Dynamics Centre for Doctoral Training:
Alvise, \cm{George}, \cm{Hailey}, Oli, Sam, Sisi, Simon, Will. I learned a lot
from every one of you, and only sometimes about physics. Similar services have
been provided by Jamie, Jonny, Luke and Sam. It's sad that we can't spend more
time together, but it's always fabulous when we do. To the other
friends, from CCCBC, OURCs and elsewhere, I'm sorry that my choice of enormous
margins has meant that you didn't quite get squeezed onto this page but I
appreciate you just as much as those above.

The most welcome distraction from studying over the last four years has been
coxing on the river Thames. I am enormously grateful to the ladies and coaches
of Thames Rowing Club. You never stop impressing me, and I will miss training
and drinking coffee with you. I will not miss regularly waking up before five
o'clock in the morning.

Susie, thank you for putting up with me. You keep me going when I am down,
and never stop believing in me. I could probably have done this without you,
but I would never have wanted to.

Finally, to my parents: thank you for everything you have given me, I love you
both.
\end{singlespace}
