This impact statement is included as part of Imperial College London's policy
on studies affected by the coronavirus pandemic. It will be removed after
examination, and will not feature in the final version of this thesis.

In this thesis I will describe the creation of a microfabricated chip trap for
laser-cooled \CaF{} molecules. The original intention was to design and build
such a device, and incorporate it into the existing \CaF{} experiment that we
operatre in the Centre for Cold Matter at Imperial College.

In March 2020 I was focusing on the fabrication of the
chip trap (described in chapter~\ref{fab}), which took place in the cleanroom
facilities at the London Centre for Nanotechnology. These were closed to
external users from 19\textsuperscript{th} March -- 1\textsuperscript{st}
October, completely halting development of this key aspect of the project. When
access resumed it was limited due to the requirement to social distance. This
meant that developing the fabrication procedure for the chip was severely
delayed.

The chip experiment has been designed to integrate with the existing \CaF{}
experiment (described in chapter~\ref{overview}) however the development of
this machine was delayed by the closure of the College laboratories starting on
18\textsuperscript{th} March. Since the existing experiments were not
sufficiently developed, and priority was given to other experiments using the
same apparatus, it was impossible to install the chip chamber. 

The combined result of these two effects was that the molecule chip experiment
was not fully implemented, and we were limited to the preliminary experiments
which are reported in chapter~\ref{exper}. The fabrication was completed, but
only to the point of implementing a single-layer trapping chip, without
integrated microwave guides. During the lab closures, the simulations in
chapter~\ref{sim} were conducted, and the chip design was improved, but this
effort was not sufficient to fully mitigate these considerable delays.
