% Could have mentioned ion chips. Reviews:
%\cite{RevModPhys.62.531}
%\cite{Romaszko2020} (mostly chips?) -- I actually do use this one...

Recently, there has been great progress in the production of ultracold
molecules by direct laser cooling and trapping~\cite{Fitch2021}. On the whole,
progress in this field has followed the existing roadmap of atomic experiments,
from laser slowing, to magneto-optical trapping, to optical dipole trapping.
Another cold atom experiment, the chip trap, does not yet have a molecular
analogue. As we will see below, this tool has proven to be of great use as a
robust, compact and portable device for cold atom experiments. A molecular
counterpart could prove equally invaluable, and could provide capabilities
beyond those of atom chips.  This could include strong coupling to on-chip
microwave fields and  the realisation of a cavity quantum electrodynamics
system, exploiting the stable rotational states of molecules and their strong
electric dipole coupling to resonant microwave fields.

The molecule chip was originally proposed by Andr\'e et al.~\cite{Andre2006} as
a means of leveraging the long coherence times of a diatomic molecule in
combination with robust control using on-chip microwave guides. In this
proposal a single molecule is trapped in the near field of a resonator, which
can be used for state control and readout. The built-in integration with
microwave photons would allow the exchange of information via a flying qubit,
either to other devices on the same chip, or to other separate devices.
%
It is possible to envision how such a device is scalable, and could be used to 
interact with other quantum devices that operate in the microwave regime, such
as superconducting charge qubits.

At the time of this proposal, the field of ultracold molecules was in its
infancy. Today it is possible to create dense clouds of ultracold molecules,
which are ripe for loading onto a chip trap. In this thesis I will describe the
work that has been undertaken to implement such a device. This chapter will
further motivate my research, starting with a review of cold atoms, to atom
chips and then cold molecules. I will then summarise the motivation for a
molecule chip and outline the structure of the thesis.

\section{Ultracold atoms}
\label{intro:atoms}

Laser cooling of atoms is a developed field, with the 1997 Nobel Prize in
Physics having been awarded to Cohen-Tannoudji, Chu and Phillips for
`development of methods to cool and trap atoms with laser
light'~\cite{RevModPhys.70.721}. This subject is reviewed in various texts, with
the canonical reference being Metcalf and van der Straten~\cite{Metcalf1999}.
Here I will give a brief qualitative overview of the topic and its many
applications in modern physics, which include quantum information,
communication and metrology. Further details on these cooling mechanisms are
given in section~\ref{theory:cooltrap}.

In a typical laser slowing experiment, the forward velocity of a beam of atoms
is reduced by resonant, counter-propagating laser light. An atom can absorb a
photon from the laser and, upon spontaneous re-emission, this photon has no
preferred direction of travel. Over a large number of these photon scatters the
result is a net reduction in the forward velocity of the
atoms~\cite{PhysRevLett.40.1639}. This principle of slowing with radiation
pressure was first observed by Wineland et al.~\cite{PhysRevLett.40.1639} in
\Mg{} ions, but one of the key goals of laser slowing was to reduce the
velocity of a beam of neutral atoms (produced in, for example, an oven) as was
achieved by Andreev et al.~\cite{Andreev1981}.

A further goal was to reduce the velocity even further, so that the slowed atoms
could be loaded into a magnetic trap.  To achieve this it is essential to
account for the change in the resonant frequency of the atoms due to the
Doppler shift that occurs as the atom's velocity is reduced. Phillips and
Metcalf~\cite{PhysRevLett.48.596} were able to achieve this for \Na{} atoms by
the Zeeman slowing technique, where a changing magnetic field across the
beamline is used to ensure the relevant transition is always resonant with the
light. Later the same group would achieve the same effect by chirping the
frequency of the light~\cite{Prodan1984}, so that the light is sufficiently
red-shifted to be resonant with the atoms as they slow down.  Such experiments
must take place under ultra high vacuum to prevent loss by collisions with a
background gas.

Another key development was the implementation of the magneto-optical trap
(MOT) where atoms were confined by a quadrupole magnetic field and red-detuned
laser light incident from every direction. This scheme is designed so that
atoms that are away from the trap centre experience a Zeeman shift that brings
them into resonance with the light. The polarisations are then chosen so that
the atom will preferentially scatter photons from the beam that produces a
restoring force towards the trap centre. This results in a much stronger
restoring force than in a pure magnetic trap, and also produces a
velocity-dependent damping to reduce the temperature of the atoms. This was
first implemented by by Raab et al.~\cite{PhysRevLett.59.2631}, also in \Na{},
although subsequently many different species have been laser-cooled and
confined in a MOT.

Due to the stochastic nature of photon scattering, there is a fundamental limit
on the lowest temperature that can be achieved using just the Doppler cooling 
mechanism.  Early studies of Doppler cooling in a 3D optical molasses
found that in fact, anomalously low temperatures
were reached~\cite{Lett1988}. This was eventually explained by
Dalibard et al.~\cite{Dalibard:89} as being due to sub-Doppler cooling
mechanisms, which rely on polarisation gradients set up in the light field.
This reduced the atom temperature close to the recoil limit, which is
related to the energy imparted by a single photon scatter.

Once the atoms are cooled to sub-millikelvin temperatures, it becomes possible
to trap them without dissipation, that is in a conservative trap. Two main
types have become popular -- the magnetic trap and the optical dipole trap. In
a magnetic trap, atoms are pumped into a weak-field seeking state, and trapped
at a local magnetic field minimum, such as can be created, for example, by a
pair of anti-Helmholtz coils~\cite{PhysRevLett.54.2596}. In an optical dipole
trap atoms are confined by intense, far-off-resonant light~\cite{Chu1986}. This
light induces an a.c.\ Stark shift, which produces an attractive potential
towards the region where the light's intensity is greatest.

For a sufficiently tight optical dipole trap, an optical tweezer is formed,
where a single atom can be trapped and easily manipulated by controlling the
light~\cite{Schlosser2001}. A series of tweezer traps can be used to form a
lattice of traps~\cite{Schlosser2001}, with individually-trapped atoms able to
interact with each other by dipole-dipole interactions. A lattice can also be
formed in a standing wave optical trap (SWOT), where light reflected from a
surface creates a series of local field maxima for trapping of
atoms~\cite{Wu2017}.

Inside a magnetic or optical dipole trap it becomes possible to cool beneath
even the recoil limit by evaporative cooling, where the hottest atoms are
ejected from the trap. The remaining atoms thermalise at a lower temperature
than the original cloud. This technique was employed by Anderson et
al.~\cite{Anderson198} to cool \esRb{} to sufficiently low temperature and
density to form a Bose-Einstein condensate (BEC), earning Cornell and Wieman a
share of the 2001 Nobel prize. This prize was also shared with Ketterle, who
undertook similar work with \Na{} atoms~\cite{PhysRevLett.75.3969}.

With this ability to reliably create low-temperature atomic clouds (or even a
single cold atom) confined in traps and lattices, comes the ability to create
quantum devices for simulation, communication and metrology, with promises of
future applications in quantum computing. Coherent control of atoms in optical
lattices for simulation has been demonstrated~\cite{Schafer2020}, and optical
lattice clocks have become the cutting edged in
timekeeping~\cite{PhysRevX.8.021036}. There are numerous examples of atoms
being used for precise sensing, for example, acceleration~\cite{Chen2019}
including gravity~\cite{Stray2022}. Cold atoms can also be employed to
explore fundamental physics, such as the search for dark
matter~\cite{Wcislo2018}. Future experiments also plan to utilise cold atoms
for new gravitational wave detectors operating in frequency bands that are
inaccessible to existing detectors~\cite{Badurina_2020}.

These experiments, and those like them, have been made easier by technological
developments such as atom dispensers, which remove the need to cool
a hot beam of atoms, and vapour cells, which can entirely remove the
need for a complicated vacuum system. This has led the way to miniaturisation
and scalability of cold atom experiments, which is an active field of research.
The complexity of these experiments can be further reduced by using, for
example pyramid~\cite{Lee:96}, mirror~\cite{Reichel1999, 4797887} or
grating~\cite{Nshii2013} MOTs, where some of the MOT light beams are produced
by reflection or diffraction from a surface. These are strongly linked to the
main focus of this thesis: the chip trap.

\section{Chip traps}

The chip trap was proposed as a mechanism for studying atoms in very
high-gradient magnetic traps~\cite{PhysRevA.52.4004}, but it has evolved into a
useful tool for miniaturised and robust cold atom experiments. These can be
integrated with, for example, microwave components, to form hybrid quantum
systems. Further details will be presented in section~\ref{theory:chips}, but
here I will give a brief overview of the operating principles and history of
atomic chip traps. I will also explain why loading molecules onto a chip may be
a useful development of these experiments.

We have already discussed the idea of trapping atoms in a quadrupole magnetic
field using macroscopic current-carrying coils. It is also possible to generate
magnetic traps from the field of a wire combined with a homogeneous bias field.
In a chip trap experiment, the wires are positioned on the surface of a
substrate, and can be made very small (on the scale of a few microns) by the
use of common microfabrication techniques. Various microscopic atom traps were
pioneered by by H\"ansch and Zimmermann at the Max Planck Institute of Quantum
Optics (MPQ) and T\"ubingen~\cite{PhysRevLett.80.1634, PhysRevLett.81.5310}, as
well as in Harvard~\cite{Drindic1998}. This was followed by work in Innsbruck,
where \Li{} atoms were guided using a two dimensional trap formed with a
free-standing wire~\cite{PhysRevLett.82.2014}. 

The first true chip traps, operating in three dimensions were reported by the
MPQ group~\cite{Reichel1999}, who also implemented a mirror-MOT for loading
\esRb{} into their traps. This was shortly followed by developments in
controlling and guiding \Li{} atoms trapped above a chip's
surface from Innsbruck~\cite{Folman2000}.
%
Atom chips were soon found to be a robust tool for cold atom experiments,
including the production of BECs, with groups from the Ludwig Maximilian
University of Munich and T\"ubingen both reporting \esRb{} BECs at the same
conference in 2001~\cite{Hansel2001, Ott2001}. Since then atom chips have been
used to investigate lower dimensional gasses, as reported in
\inlinerefs{PhysRevLett.116.030402, Hofferberth2007, Yuen2015}, and have found
uses in various other experiments as a convenient method of preparing cold
atomic clouds~\cite{PhysRevLett.104.073604}.
%
This includes experiments creating non-classical spin-squeezed states (see
chapter~\ref{squeeze}), implementing magnetic lattices~\cite{Gerritsma2007} and
performing interferometry~\cite{Wang2005}.

2004 saw the first implementation of an on-chip Michelson interferometer, based
on the creation, splitting and guiding of BECs all on a chip. In the same year,
the prospect of integrated atom chip devices was fully realised at the National
Institute of Standards and Technology, where a compact and portable atomic chip
clock was developed~\cite{Knappe2004} based on the hyperfine transitions in
\Cs{}. This has since become a commercial product with uses across a variety of
fields, such as military and space science~\cite{RAMIREZMARTINEZ2011247}
including an atom chip experiment conducted on board the International Space
Station~\cite{Frye2021}.

Also in 2004, it was demonstrated by the MPQ group that coherence times of
around \SI{1}{\second} could be achieved for \esRb{} atoms held in a chip trap
within \SI{100}{\micro\meter} of the surface~\cite{Treutlein2004}. In this
experiment microwave fields were used to drive hyperfine transitions in the
molecules, with the microwave radiation delivered from an external source. This
was soon extended to experiments where the microwaves were delivered by on-chip
microwave components built on a two-layer device~\cite{Treutlein2008,
Boehi2009}, with a view to develop a microwave trap and perform quantum
gates entirely on-chip.

The work of the Munich group built towards coherent control of an atom coupled
to on-chip microwaves, however a more ambitious goal is the coupling of an atom
to a microwave cavity, which can lead to powerful control over the spin system
by leveraging the effects of cavity quantum electrodynamics. One requirement of
this is so-called strong coupling between the microwave photons and the atomic
transition, which is challenging due to the comparatively small transition
matrix element of the hyperfine transitions in the atoms, and the need for a
high quality microwave cavity. The latter of these, as we will discuss in
chapter~\ref{mws}, requires the use of superconducting microwave components.

A superconducting atom chip is an attractive idea, since as well as the
potential for low-loss microwave components, superconducting wires can produce
deeper magnetic traps. The first such device was first realised by
Haroche's group in Paris in 2006~\cite{Nirrengarten2006}, with a BEC on a
superconducting chip following in 2008~\cite{Roux2008}. Similar superconducting
wire traps were used to investigate the Meissner
effect~\cite{PhysRevLett.101.183006}, and subsequent development of these
superconducting atom chips lead to full quantum control of an atom cloud held
in place above a superconducting microwave resonator~\cite{Bernon2013}. Here
the resonator was designed to be off the atomic resonance, so that the internal
state of the trapped atoms were unaffected by its presence. Of additional note
in this paper is the loading scheme used for the chip -- an optical tweezer is
used to bring the atoms from a room-temperature environment to within
\SI{400}{\micro\meter} of the chip surface, before being transferred to
surface-based microtraps.

A later experiment~\cite{Hattermann2017} would see the coupling of atoms to the
microwave resonator, realising a hybrid atom-microwave system, and the
investigation of microwave cavity quantum electrodynamics. Rabi oscillations
between hyperfine transitions could be driven, but strong coupling was not
realised. It has been possible to couple atoms strongly to monolithic
microresonators~\cite{Aoki2006}, but only in free fall, not whilst trapped.
Other efforts to reach this strong coupling regime come from Hogan's group, who
use Rydberg atoms, utilising the enormous electric dipole moment of the
transition to achieve stronger coupling~\cite{PhysRevLett.124.193604}. Again,
such experiments are performed with atoms that are in flight, and in this case
travelling at supersonic speeds.

An improvement to such experiments would be to confine the atom close to the
microwave field, near the anti-node of the resonator to maximise the coupling
strength. However, another potential method is to use a molecule with high
electric dipole moment instead of a Rydberg atom. Recent advances in the
laser-cooling and trapping of diatomic molecules make these an exciting
prospect for implementing a microwave cavity QED device, as was originally
proposed by Andr\'e et al.~\cite{Andre2006}. In the next section we will
briefly review this field, before further outlining the prospects for a
molecule chip trap.

\section{Ultracold molecules}

There are a number of potential benefits that can come from cooling molecules
rather than atoms. As already mentioned, molecules have a rich energy
structure, including the rotational states. These are closely-spaced energy
levels of opposite parity, with strong electric dipole transitions between
them. Hence, molecules are far more polarisable than atoms and couple strongly
to d.c.\ electric fields and resonant microwave fields, and also to one another
through their dipole-dipole interactions.
%
Molecules also allows the investigation of fundamental physics, such as the
measurement of the electron's electric dipole moment, which has helped to
constrain particle physics theories that go beyond the standard
model~\cite{ACMEreview}.

The energy structure of molecules is far richer than that of atoms; a diatomic
molecule will have both vibrational and rotational energy levels, which can be
leveraged for novel imaging schemes, strong coupling to microwave transitions,
amongst other applications. However these introduce additional complications
that make experiments with ultracold molecules more challenging than their
atomic equivalents.

There are two main schools of ultracold molecule experiments. In the first of
these gases of cold atoms are used to synthesise cold molecules, usually by
association via a Feshbach resonance~\cite{PhysRevA.89.033604}.  In this thesis
we will focus on the second school: direct cooling of hot diatomic molecules.
The first experiment to successfully trap molecules was reported by Weinstein
et al.~\cite{Weinstein1998}, who created calcium monohydride (\CaH{}) molecules
by laser ablation, and then cooled them to below the depth of a magnetic trap
by buffer-gas cooling. In this technique, an inert buffer gas is used as an
intermediary to thermalise the molecules with a cold copper cell typically held
at a few kelvin.
%
An alternative technique to slow a beam of molecules was developed in Gerard
Meijer's group, who used Stark deceleration to first slow a beam of carbon
monoxide~\cite{Bethlem1999}, and later to slow then electrostatically trap
ammonia in both a quadrupole trap~\cite{Bethlem2000} and a storage
ring~\cite{Crompvoets2001, Crompvoets2005}. However these methods produce
molecules that are orders of magnitude warmer than the atoms produced by laser
cooling.


Buffer gas cooling has become a staple of cold molecule experiments, being
routinely used in the production of slow, high-flux molecular
beams~\cite{Maxwell2005, Patterson2007, Barry2011}.  Optical cycling in a
diatomic molecule with the potential of laser slowing was first seen using
strontium monofluoride (\SrF{}) by DeMille's group~\cite{Shuman2009}. To
account for the more complex energy structure of the molecule, additional
lasers were used to repump the molecule from states that were dark to the
cooling transition.  Despite this difficulty, the DeMille group had soon enough
applied the technique to achieve laser-slowing~\cite{PhysRevLett.108.103002}
and eventually an \SrF{} MOT in 2014~\cite{Barry2014, PhysRevLett.116.063004}.
The initial report boasted temperatures of \SI{2.5}{\milli\kelvin} and
there was scope to reduce this further.

Alongside the development of laser-cooling \SrF{}, there have been developments
in the laser-cooling of various other molecules, notably yttrium oxide (\YO{}),
ytterbium monofluoride (\YbF{}) and calcium monofluoride (\CaF{}), the latter
being the main molecule of focus in this thesis. \YO{} has been trapped in a
MOT, stored in a lattice and cooled to the order of a micro
kelvin~\cite{PhysRevLett.127.263201}. \YbF{} has been used in various
experiments to measure the electric dipole moment of the
electron~\cite{Hudson2011}, and it is hoped that laser-cooling could be a
method for further improving the precision of this experiment~\cite{Fitch2020}.
Meanwhile, \CaF{} shows promise as a molecule of interest for investigating
quantum information and the fundamentals of quantum chemistry. Laser-slowing of
\CaF{} was first observed in the Centre for Cold Matter (CCM) at Imperial
College London~\cite{PhysRevA.89.053416}, where a supersonic beam was slowed by
\SI{20}{\meter\per\second} using a chirped beam of light. The \CaF{} experiment
was further developed with the implementation of a buffer gas source for
\CaF{}~\cite{Truppe2018}, with further developments in laser slowing coming
from both CCM~\cite{Truppe2017a} and the Doyle group in
Harvard~\cite{0953-4075-49-17-174001}.

A \CaF{} MOT was first reported by CCM~\cite{Williams2017} in 2017, followed by
the Harvard group~\cite{PhysRevLett.119.103201}. These experiments took
slightly different approaches to avoid the pumping of molecules into dark
states: the Imperial College group used a dual frequency
technique~\cite{TarbuttandSteimle}, while the Harvard group used an r.f.\
switching technique that was first developed in Jun Ye's group at
JILA~\cite{PhysRevLett.110.143001}.  The \CaF{} MOT has opened the door to
experiments with large clouds of \CaF{} molecules, with today's MOTs capable of
loading $\sim10^5$ molecules~\cite{PhysRevLett.119.103201}. The temperatures of
these clouds can be further reduced to below the Doppler
limit~\cite{Truppe2017, PhysRevLett.123.033202} and can then be further trapped
and controlled by some of the same techniques already discussed above for
atoms. This includes confinement in magnetic traps~\cite{WilliamsMagnetic2018}
and in an optical dipole trap and lattice~\cite{Anderegg2019a}. Further cooling schemes such as
transverse cooling (similar to that seen for \YbF{} in \inlineref{Alauze2021})
and Zeeman-Sisyphus cooling have been demonstrated~\cite{Fitch2016,
PhysRevLett.127.263002}.  Combining these various schemes with ongoing research
into collisions with atoms~\cite{PhysRevLett.126.153401} and sympathetic
cooling could see even lower \CaF{} temperatures achieved in the near future.

\CaF{} has shown to have promise in quantum information and simulation, with
coherent control in a magnetic trap having been
demonstrated~\cite{WilliamsMagnetic2018, Blackmore_2018} with coherence times
of over \SI{1}{\second} plausibly achievable~\cite{PhysRevLett.124.063001}.
Coherent control of the molecule has also been demonstrated in a dipole
trap~\cite{PhysRevLett.127.123202}, showing that there is significant potential
for the implementation of quantum simulations and computing. Further novel
schemes for molecule-based quantum information have been proposed, such as
those described for topological quantum computing in \inlineref{Micheli2006} or
for the implementation of qudits in \inlineref{Sawant_2020}.

Another topic of interest is collisions between cold molecules and cold atoms.
This has recently been observed in \NaLi{} molecules by Son et
al.~\cite{son2019collisional}, and in \CaF{} at Imperial
College~\cite{Jurgilas2021, JurgilasPRL_2021}. The thermalisation of molecules
with atoms could lead to further temperature reduction by sympathetic cooling,
which may be enhanced in a dipole trap. It also paves the way for
investigations into quantum chemistry at a very fundamental level. Recent
research into the production of polyatomic MOTs by the Harvard
group~\cite{Vilas2021} will no-doubt also play an important role in
such investigations.

To summarise, research into ultracold molecules is rapidly developing, with
methods for producing cold, dense clouds of diatomic molecules already
available. The rich energy structure of molecules makes them a promising
candidate for use in quantum information, communications and sensing
experiments including in chip-based devices.

\section{Molecule chip trap}

We have seen in the above discussion that ultracold molecules can be a useful
tool in quantum information and simulations. Further, recent developments in
cooling techniques mean that we are now able to produce dense clouds of
molecules such as \CaF{}, which exhibit long coherence times in magnetic traps.
Various techniques that have been applied to cold atoms have been equally
successfully applied to cold molecules, but a conspicuous absence in the
preceding discussion is a chip trap for ultracold molecules.

Such a device is of significant interest, since it provides a robust and stable architecture for quantum experiments could
prove extremely useful when applied to cold molecules. In addition to the
magnetic traps discussed above, polar molecules can be
contained in electrostatic traps, which could be leveraged to construct traps
similar to existing ion chip traps~\cite{Andre2006, Romaszko2020}. Such devices
are inherently scalable, with the ability to constrain multiple molecules at
various sites across the chip surface. They can then be transported by changing
the electric potentials, which simply amounts to changing the voltages on
trapping electrodes.

Another benefit of a molecule chip system is that the rotational transitions in
a diatomic molecule can couple very strongly to microwave fields, much more so
than the hyperfine transitions in atoms. Andr\'e et al.~\cite{Andre2006}
propose that building a molecule chip with integrated microwave guides, similar
to equivalent atom chips reported in \inlineref{Nirrengarten2006}, could
produce powerful tools for quantum information and communication. Amongst these
are the ability to carry out a non-demolition measurement of the molecule
state. This, along with the ability to drive microwave transitions using the
guide, allows the device to be totally self contained -- once molecules are
loaded all interactions can be performed electrically. The long-lived
rotational states of \CaF{} make this molecule a promising candidate for such a
device.

Along with readout, strong coupling to a resonator could allow for the
implementation of a novel sideband cooling scheme to reduce the molecule's
motional energy to the ground state of the trapping potential. It would also be
possible to couple molecules on neighbouring trapping sites using the resonator as a bus.
Similarly it may be possible to extend the interaction to longer ranges, since
photons can be used as flying qubits to couple quantum mechanical systems over
long distances. The schemes mentioned in this section will be explored further
in chapter~\ref{mws}.

There has been some work investigating molecules trapped close to chips, mainly by
the Meijer group, who have designed and implemented microfabricated Stark
decelerators~\cite{Meek2008}, and even trapped molecules on a
chip~\cite{Meek2009}. However, similar to their other work, these molecules are
much hotter than can be achieved with laser-cooling.

This thesis describes the work that has been undertaken in CCM to build a
microfabricated chip trap for \CaF{} molecules at ultracold temperatures. I
will outline a design inspired by existing atom chips, and the proposals in
\inlineref{Andre2006}. This design will provide a stepping stone towards more
advanced devices, which can implement the various schemes described above. It
will integrate with the existing experiment, and take advantage of the
properties of \CaF{}, including the long coherence times of rotational
transitions that can be achieved in magnetic traps.

\section{Structure of the thesis}

In chapter~\ref{theory} I will introduce key background theory: 
laser-cooling of simple systems, the operation of chip traps, and the physics
of diatomic molecules. Next, chapter~\ref{overview} gives an overview of the
existing \CaF{} experiment, as well as some particulars of the laser-cooling
methods used specifically for \CaF{}. Here I will also outline the new chip
experiment, and how it will integrate with the existing apparatus. We have
studied the loading procedure for the trap with simulations, and these are
presented in chapter~\ref{sim}.

I microfabricated chip traps, as will be discussed in chapter~\ref{fab}, and
then loaded these into a vacuum chamber for initial testing. This included
testing that the current capacity of the trapping wires was as expected, that
ultra-high vacuum could be reached, and that it will be possible to image
molecules without too much background scatter created by the chip. These tests,
and a scheme to reduce the background scatter are discussed in
chapter~\ref{exper}. Chapter~\ref{mws} describes how a microwave guide and
resonator can be implemented as part of the experiment, as well as the
behaviour of a single molecule coupled to a microwave cavity. I will extend
this idea for ensembles of molecules coupled to a cavity in
chapter~\ref{squeeze}, where I propose a scheme to use a quantum non-demolition
measurement to create a spin-squeezed state in such an ensemble. Finally,
chapter~\ref{outlook} describes the future prospects for this project.
