\cm{It might make sense for this section to become a chapter of its own right.}

\subsection{Laser cooling of atoms}

A brief discussion of laser cooling is presented here. More detailed discussion
can be found in references~\cite{Metcalf1999,RevModPhys.70.721,McCarron_2018}.

The basic principle of laser cooling of atoms is to deflect atoms from their
trajectory by transfer of momentum from the laser light (radiation
pressure).~\cite{RevModPhys.70.721} Consider a moving atom with a
pre-chosen cooling transition between two internal states.  When such an atom
encounters a counter-propagating resonant photon, absorption can take place,
reducing the atom's momentum. The atom can re-emit the photon in any direction,
but on average the resulting atom will be slower than before the encounter.
This process is known as Doppler cooling, as the light must be detuned from
resonance to account for the Doppler shift experienced by the moving
molecule.~\cite{Metcalf1999}

Of course, the assumption of a two-level system is a simplification. A key
example is sodium, where the transition $3S_{1/2}\, (F=2) \rightarrow 3P_{3/2}\,
(F'=3)$ was used to demonstrate this technique. However, since the excited
states of sodium have decay channels into $F=1$, it is possible for atoms to
fall into this state and out of resonance with the cooling
transition.\footnote{To be precise, $F'=3$ has no decay channels to $F=1$, but
off-resonant excitation into $F'=2$ can result in the population of dark states
by the decay $F'=2 \rightarrow F=1$. The repump operates on $F=1\rightarrow
F'=2$.} This can be overcome by introducing repumping light to transfer atoms in
dark states back into bright states.~\cite{RevModPhys.70.721} \cm{figure?}

We will foucs on atomic sources that produce a beam, with typical velocities of
a few \SI{100}{\metre\per\second}.~\cite{Metcalf1999}  As the atoms are slowed,
the Doppler shift they experience will change, and hence they will move out of
resonance with the transition.~\cite{RevModPhys.70.721} This can be overcome by
introducing chirped light, so that the frequency of the cooling light varies
across the lenght of the beam.~\cite{Prodan1984} In contrast, the Zeeman slower
applies a varying magnetic field. to shift the transition frequency of atoms
along the beam while the frequency of the light is kept the same.

An optical molasses can be formed from a pair of counter-propagating laser
beams, both red-detuned from the cooling transition. This means that if an atom
moves towards either beam it will undergo Doppler cooling.  A set of three
perpendicular optical molasses can cool an atom in each direction, reducing the
temperature but not providing any trapping force~\cite{Metcalf1999} . Further
cooling can be achieved in an optical molasses by choosing the polarization of
the light such that there is a polarization gradient. This sub-Doppler cooling
allows atoms to be cooled to the lowest limit, the recoil temperature of the
atoms (typically a few microkelvin).~\cite{Dalibard:89}

Trapping can be achieved (for example) by optically pumping the atoms into a
weak-field seeking state and applying a magnetic field to form either a
quadrupole~\cite{PhysRevLett.54.2596} or
Ioffe-Pritchard~\cite{PhysRevLett.51.1336} trap. \cm{Magnetic trapping is
discussed further in section~\ref{chiptraps}.} Magnetically trapped atoms can be
further cooled by evaporation, which can ultimately be used to form a
Bose-Einstein condensate.~\cite{Anderson198} A quadrupole trap combined with an
optical molasses forms a magneto-optical trap (MOT) in which atoms are
simultaneously trapped by the magnetic field and cooled by the
lasers.~\cite{PhysRevLett.59.2631}

The MOT has become a fundamental component of many cold atom experiments, a vast
field which we cannot explore in any level of detail here. Of particular note to
us are experiments involving dipole trapping~\cite{PhysRevA.47.R4567}, such as
those in an optical lattice~\cite{Bakr2009} or tweezer~\cite{Ashkin:86}. Control
of the atomic states in a lattice has been used to precisely realise the
second~\cite{PhysRevLett.120.103201} and to perform quantum
simulation~\cite{Gross995}.

\subsection{Laser cooling of molecules}

The rich energy structure of molecules, having rotational and vibrational
degrees of freedom, makes cooling procedures more involved~\cite{Tarbutt2018,
1367-2630-17-1-015007}, but there are numerous properties of molecules that
could be exploited in a range of applications. The large electric dipole moment
of some diatomic molecules means that they interact more strongly with electric
fields than atoms, making an optical lattice of molecules, or a molecule on a
chip, a good candidate for scalable quantum simulation or
computing~\cite{Micheli2006, Andre2006}.  Collisions between cold molecules
could allow investigation of the nature of quantum chemistry~\cite{Krems2008},
and cooled \YbF{} is being developed to precisely measure the electron electric
dipole moment as a means of testing fundamental theories of
physics~\cite{Lim2018}.

The tools developed for creation of cold atoms can be directly applied to
producing cold molecules. A MOT of \esRb{} and \ottCs{} can be used to form
\RbCs{} via an interspecies Feshbach resonance~\cite{PhysRevA.85.032506,
PhysRevA.89.033604} and then transferred into the ro-vibrational ground state by
stimulated Raman adiabatic passage.~\cite{PhysRevLett.113.255301,
RevModPhys.70.1003}.

Direct laser cooling of molecules can be challenging due to the complex energy
structure. The presence of numerous decay channels means that many repumping
beams can be required to keep molecules in bright states. One way to avoid use
of lasers is to slow molecular beams with a Stark decelerator, which removes
energy from dipolar molecules by varying an electric field across the
beam.~\cite{Bethlem1999} However the energy structure of some molecules makes
them good candidates for laser cooling.~\cite{Shuman2010,}
\cm{I want to find a good cite here that lists candidate molecules for laser
slowing...}

\cm{Should I mention dual-frequency or rf mots?} Beams of \SrF{} and \CaF{} have
been slowed with chirped light~\cite{PhysRevLett.108.103002, Truppe2017a} and
held in a MOT~\cite{Barry2014, Williams2017}. Sub-Doppler
cooling~\cite{Truppe2017} and coherent control of the rotational state have been
demonstrated for \CaF{}.~\cite{Williams2018, Blackmore_2018} \cm{And also for
other mols?} Early experiments with optical tweezers have also been
performed.~\cite{Anderegg2019}

\cm{Will need to re-visit these last two paras as these experiments will
have progressed. Also can probably sort cites}

Ongoing experiments with \CaF{} aim to achieve an increased phase space density by
sympathetic cooling with \esRb{} in a dipole trap.~ Recent
work has also discovered two vibrational transitions which are highly
insensitive to a magnetic field, making them ideal candidates for a qubit
transition in a molecule chip.
